Token-level author diarization using clustering of stylistic contexts

### 2017-06-01 paper/paper.tex
Setup for tasks a and b.

>>>>

In task \emph{a}, we used 50\% of dataset as a training set, and other half as a test set. Since this task is characterized as an outlier detection task, we tested an isolation forest algorithm, but achieved poor results. Other algorithms which we evaluated were Gaussian mixtures and hierarchical agglomerative clustering. Agglomerative clustering with cosine affinity and average linkage achieved the best performance on the training set and we report its result on the test set. We measured macro $F_\mathrm{M}$.

In task \emph{b} we also split dataset in two half. Grid search for the best hyperparameters was performed for agglomerative clustering. The best performance on the training set was obtained with euclidean affinity and average linkage.

For task \emph{c}
